What We Eval in the Shadows

### 2021-04-15 paper/main.tex
A bit of a conclusion

>>>>

In this paper we provide large-scale study of the use of the \eval function in
the R programming language. It is based primarily on a corpus of
\CranRunnableScripts scripts extracted from \CranPackages R packages. As
expected, \eval is used mainly in libraries and therefore we have found just a
few \eval call sites in scripts coming from Kaggle that we included to
represent code written by R practitioners. We used an instrumented version of
the R virtual machine, \rdyntrace, to capture all \eval calls traces
including the relevant side effects that happen within these calls. There is a
number of insights that can be learnt from the data.
%
\eval is widely used in the R core packages that come bundled with the
language. Because of that there is hardly any R code that would not use it.
\eval is used to implement some basic functionality such as package loading.
Putting the core packages aside, in CRAN, \eval is used by \PkgPackagesRatio
of the available \CranPackages packages.
%
The code executed by R \eval has unusual expressive power. It can essentially
modify anything anywhere which is wary for both R developers as well as R
compiler.
% TODO expressions passed to eval
% TODO side effects

% how much can we say about the threat model?
